---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
setwd(here::here())
```


# Installation

The `cdyns` package can be installed with the following script:

```{r installation, eval = FALSE}
#install.packages("remotes")
remotes::install_github("aterui/cdyns")
library(cdyns)
```

# Overview

The R package `cdyns` is a collection of functions to perform community dynamics simulations with stock enhancement. The current version of the package includes the following functions:

-   `cdynsim` : Community dynamics simulation with stock enhancement

# Instruction

## Basic usage

The key arguments are `n_timestep` (the number of time step to be saved), `n_warmup` (warm-up period during which seeding happens), `n_burnin` (burn-in period for eliminating initial condition effects), and the number of species in a community (`n_species`). The community dynamics are simulated using either a Ricker equation (`model = "ricker"`) or a Beverton-Holt equation (`model = "bh"`).

Sample script:

```{r}
library(cdyns)
sim <- cdynsim(n_timestep = 1000,
               n_warmup = 200,
               n_burnin = 200,
               n_species = 10)
```

This script returns the following:

-   `df_dyn`: dataframe for dynamics. Columns include time step (`timestep`), species id (`species`), and density (`density`)

-   `df_community`: dataframe for the whole community. Columns include a temporal mean (`mean_density`) and sd (`sd_density`) of the whole community density.

-   `df_species`: dataframe for species density and traits. Columns include species id (species), temporal mean (`mean_density`) and sd of species density (`sd_density`), carrying capacity (`k`), intrinsic population growth rate (`r`), and interspecific competition coefficient with the stocked species (`alpha_j1`).

-   `interaction_matrix`: matrix of intra- and interspecific interactions.

```{r}
print(sim)
```

## Stock enhancement

Stock enhancement can be added using `stock` argument. For example, `stock = 100` adds 100 individuals to species 1 every time step:

```{r, eval = F}
sim <- cdynsim(n_timestep = 1000,
               n_warmup = 200,
               n_burnin = 200,
               n_species = 10,
               stock = 100)
```
